Accelerated convergence of convective simulations using boundary value problems

### 2017-12-19 tex/bvp_paper.tex
puts figures into paper

\subsection{The Boundary Value Problem}
The Boussinesq BVP is simply the time-stationary, horizontally- and time- averaged equations
of hydrostatic balance and energy conservation,
\begin{gather}
\frac{\partial}{\partial z}\angles{\varpi} = \angles{T_1}\hat{z},
	\label{eqn:bouss_BVP_momentum}
\\
\frac{\partial}{\partial z}\angles{wT_1} = \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1},
	\label{eqn:bouss_BVP_energy}
\end{gather}
where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  These
equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}-\ref{eqn:bouss_energy})
and neglecting terms that vanish due to symmetry in the evolved flows.  Convective flows
are perturbations around a thermal profile defined by these equations in the proper evolved state.

In Boussinesq RBC, the thermal structure of the atmosphere is fully determined by the specification
of the convective flux, $F_{conv} = \angles{w T_1}$.  If this profile is known, then $T_1$ and
$\varpi$ can be found under the proper specifications of boundary conditions.  
Under the choice of mixed thermal boundary conditions, the initial
atmosphere contains more thermal energy ($\propto T$) than the 
evolved adiabatic solution.  As the atmosphere adjusts to be nearly isothermal in the interior,
it must evolve towards the (cold) temperature value specified at the upper boundary.
The evolution of the atmosphere results in an asymmetric flux profile during 
the slow thermal evolution of the atmosphere.  Furthermore, under our nondimensionalization,
the convective flux (and the flux at the upper boundary layer) are O(1) during the convective
transient, whereas the flux entering the atmosphere at the lower boundary is O(Ra$^{-1/2}$), so the asymmetry of the fluxes
becomes increasingly pronounced as Ra is increased into the turbulent realm.

@@

In essence, solving the BVP is equivalent to saying that even though the magnitude of flux through
the system is not initially correct, the system appropriately picks out the ratios
\begin{equation}
f_{\text{conv}} = \frac{F_{\text{conv}}}{F_{\text{tot}}}\qquad
f_{\text{cond}} = \frac{F_{\text{cond}}}{F_{\text{tot}}}.
\end{equation}
in the convective, transient state, but the total amount of flux is too large until the system
reaches the proper isotherm.

@@

>>>>

\subsection{The Boundary Value Problem}
\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{\label{fig:time_trace} }
\end{figure}

One can skip the prohibitive thermal timescale required to reach an equilibrium temperature profile
in a Direct Numerical Simulation (DNS) by coupling the DNS with a simple Boundary Value Problem
(BVP) solve. Using information about the dynamics of the convection in the atmosphere, it is possible
to skip a large portion of the thermal evolution, see Fig \ref{fig:time_trace}a\&b.

The Boussinesq BVP contains equations of hydrostatic balance and thermal equilibrium,
\begin{gather}
\frac{\partial}{\partial z}\angles{\varpi} = \angles{T_1}\hat{z},
	\label{eqn:bouss_BVP_momentum}
\\
\frac{\partial}{\partial z}\angles{wT_1} = \frac{1}{\text{Pr}\text{Ra}}\frac{\partial^2}{\partial z^2} \angles{T_1},
	\label{eqn:bouss_BVP_energy}
\end{gather}
where $\angles{A}$ represents a time- and horizontally averaged profile of the quantity $A$.  
These
equations arise from taking time- and horizontal- averages of Eqns (\ref{eqn:bouss_momentum}-\ref{eqn:bouss_energy})
and neglecting terms that vanish due to symmetry in the evolved flows.  Convective flows
are perturbations around a thermal profile defined by these equations in the proper evolved state.

In Boussinesq RBC, the thermal structure of the atmosphere is fully determined by the specification
of the convective flux, $F_{conv} = \angles{w T_1}$.  If this profile is known, then $T_1$ and
$\varpi$ can be found under the proper specifications of boundary conditions.  
Under the choice of mixed thermal boundary conditions, the initial
atmosphere contains more thermal energy ($\propto T$) than the 
evolved adiabatic solution.  As the atmosphere adjusts to be nearly isothermal in the interior,
it must evolve towards the (cold) temperature value specified at the upper boundary.
The evolution of the atmosphere results in an asymmetric flux profile during 
the slow thermal evolution of the atmosphere (Fig. \ref{fig:time_trace}c).

@@

In essence, solving the BVP is equivalent to saying that even though the magnitude of flux through
the system is not initially correct, the system appropriately picks out the ratios
\begin{equation}
f_{\text{conv}} = \frac{F_{\text{conv}}}{F_{\text{tot}}}\qquad
f_{\text{cond}} = \frac{F_{\text{cond}}}{F_{\text{tot}}}.
\end{equation}
in the convective, transient state, but the total amount of flux is too large until the system
reaches the proper isotherm.  This procedure seems to converge the atmosphere quite well
(Fig. \ref{fig:time_trace}d\&e).

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{\label{fig:pdf_comparison} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{\label{fig:temp_comparison} }
\end{figure}
